A thesis draft

### 2018-11-15 res/sections/25-Tests.tex
Add other fixes

\paragraph*{Kubernetes specifications}
A Kubernetes installation was performed in order to carry out the test above.
All the machines (master node and minions) involved had the same specifications
i.e., 4GB of RAM, 2 vCPU and 10GB of SSD storage. Nonetheless the constrained
resources, absolutely far from a real Kubernetes production environment, is
possible to notice how, even with a chain of ten elements, the average time
required to deploy an SFC is equal, if not smaller, of the time required to
deploy a Virtual Box machine on an instance with 32GB of RAM, 8 vCPU and 50GB of
SSD storage.
% graphs, talk about them

>>>>

\paragraph*{Kubernetes specifications}
A Kubernetes installation was performed in order to carry out the test
descripted above. All the machines (master node and minions) involved had the
same specifications i.e., 4GB of RAM, 2 vCPU and 10GB of SSD storage.
Nonetheless the constrained resources, absolutely far from a real Kubernetes
production environment, is possible to notice how, even with a chain of ten
elements, the average time required to deploy an SFC is equal, if not smaller,
of the time required to deploy a Virtual Box machine on an instance with 32GB of
RAM, 8 vCPU and 50GB of SSD storage.
% graphs, talk about them

\section{Final considerations}

In these tests is possible to see one critical aspect concerning an architecture
that follows the containerization approach: great flexibility in terms of
deployments. This possibility to deploy services in the form of SFCs and VNFs in
a very small amount of time is one of the key point required in the new 5G
architecture, that the tests above demonstrated this project is able to adhere.
Finally, the ability to rapidly redeploy software means smooth and easier
software development lifecycle, where developers have the possibility to
automatically push ``fresh'' software in production, letting the MANO and thus
the container orchestrator handling all the difficult and delicate tasks to put
software in a production environment, eliminating the possibility of human
errors and assuring longer uptimes.
